Inferring the Recombinant Genealogy of a Pandemic Pathogen in Real Time

### 2025-08-23 latex/main.tex
Update recombinant intervals figure

%%% TODO: Old version as placeholder. This figure is not yet finalised.
\begin{figure}[h]
    \centering
    \includegraphics[width=0.85\linewidth]{recombination_landscape.png}
    \caption{Recombination landscape. (A) Distribution of the breakpoint intervals of the 386 “robust” recombination events along the genome
(annotated with gene labels on top). Each line represents an interval colored by its size. (B) Number of overlapping breakpoint intervals (orange; left y-axis) and number of mutations along the genome (blue; right y-axis). The coordinates of the ten sites with the highest mutation counts are labeled. (C) Heatmap showing the co-occurrence counts of the parents classified by Scorpio designations. (D) Relationship between breakpoint interval size and time between the recombination event and the parental MRCA. The black curve shows the theoretical expected relationship between these quantities, estimated by minimizing the sum of squared residuals given a single parameter (the mutation rate) (STAR Methods).}
    \label{fig:landscape}
\end{figure}

>>>>

%%% TODO: Old version as placeholder. This figure is not yet finalised.
\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{recombinant_intervals}
    \caption{Recombination intervals. (A) Distribution of the breakpoint
intervals of the 356 ``robust'' recombination events along the genome
(annotated with gene labels on top). Each line represents an interval colored by its size.
(B) Number of overlapping breakpoint intervals.
(C) FIXME Heatmap showing the co-occurrence counts of the parents classified by Scorpio designations.
(D) Relationship between breakpoint interval size and time between the recombination event
and the parental MRCA. The black curve shows the theoretical expected relationship
between these quantities, estimated by minimizing the sum of squared residuals
given a single parameter (the mutation rate) (STAR Methods).}
    \label{fig:landscape}
\end{figure}
